Simulation-based and Traditional Examples using `okcupiddata` `profiles` data

### 2018-04-11 inst/doc/profiles_examples_both_methods.Rmd
Update pkgdown and inst

---
title: "Randomization and Traditional Examples using `okcupiddata` `profiles` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{OKCupid profiles example with resampling & theory-based methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

The `method = "both"` examples here do another randomization instead of using the one
with `visualize()` set to the default of `method = "randomization"`. This is to show the full
pipeline for a variety of examples, but more than likely you'll want to do something like the
following instead in practice.

@@

Randomization approach to t-statistic

@@

```{r }
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "t") ## Not needed since t implied based on variable types
  visualize(method = "theoretical")
```

@@

Randomization approach to F-statistic

@@

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "F") ## Not needed since F implied based on variable types
  hypothesize(null = "independence") %>%
  visualize(method = "theoretical")
```

@@

Randomization approach to z-statistic

@@

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>%
  hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "z") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>% 
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "z") ## Not needed since z implied based on variable types
  visualize(method = "theoretical")
```

@@

Randomization approach to $\chi^2$-statistic

@@

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since Chisq implied
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "Chisq") ## Not needed since Chisq implied
  visualize(method = "theoretical")
```

@@

Randomization approach to $t$-statistic

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing randomization
  # calculate(stat = "t") ## Not needed since t implied based on variable types
  visualize(method = "theoretical")
```

@@

Randomization approach to $t$-statistic (Not implemented)

>>>>

---
title: "Simulation-based and Traditional Examples using `okcupiddata` `profiles` data"
author: "Chester Ismay"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: kable
vignette: |
  %\VignetteIndexEntry{OKCupid profiles example with resampling & theory-based methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

The `method = "both"` examples here do another simulation-based instead of using the one
with `visualize()` set to the default of `method = "simulation"`. This is to show the full
pipeline for a variety of examples, but more than likely you'll want to do something like the
following instead in practice.

@@

Simulation-based approach to t-statistic

@@

```{r }
prof_small %>%
  specify(age ~ sex) %>% # alt: response = age, explanatory = sex
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "t") %>% 
  visualize(method = "theoretical")
```

@@

Simulation-based approach to F-statistic

@@

```{r}
prof_small %>%
  specify(age ~ status) %>% # alt: response = age, explanatory = status
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "F") %>%
  visualize(method = "theoretical")
```

@@

Simulation-based approach to z-statistic

@@

```{r}
prof_small %>%
  specify(response = sex, success = "m") %>%
  hypothesize(null = "point", p = c("m" = .65, "f" = .35)) %>% 
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "z") %>%
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(sex ~ city, success = "m") %>%
  hypothesize(null = "independence") %>% 
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "z", order = c("san fran", "not san fran")) %>%
  visualize(method = "theoretical")
```

@@

Simulation-based approach to $\chi^2$-statistic

@@

```{r}
prof_small %>%
  specify(drugs ~ status) %>% # alt: response = drugs, explanatory = status
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "Chisq") %>%
  visualize(method = "theoretical")
```

@@

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "often" = .05, "sometimes" = .25)) %>%
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "Chisq") %>%
  visualize(method = "theoretical")
```

@@

Simulation-based approach to $t$-statistic

@@

```{r}
prof_small %>%
  specify(age ~ height) %>% # alt: response = age, explanatory = height
  hypothesize(null = "independence") %>%
  # generate() is not needed since we are not doing simulation-based
  calculate(stat = "t") %>%
  visualize(method = "theoretical")
```

@@

Simulation-based approach to $t$-statistic (Not implemented)
